\chapter{Conclusion}
\section{Overview}
This report discussed the development of a small 2 player battle style game using the Unity game engine, whilst adopting an agile development methodology approach. From the beginning my main aim was to make a small battle game that would be fun and easy to play, but to also expand my knowledge when it came to games development. I wanted to be able to expand on the knowledge I had gained in making games throughout the 4 years of the software development course. In summary, the main objectives for this project was outlined as:
\newline
\begin{itemize}
\item Introduce the concept of the project
\item Provide an understanding of Game engines
\item Describe the development of the applied project
\item Make a simple, yet fun to play game
\item Dive into deeper learning into using game engines
\item Complete the project using an efficient and effective approach
\end{itemize}

From the evidence found that was discussed in chapter 6 System evaluation demonstrates that the original objects set out at the beginning have been achieved. I feel I provided a sufficient clear insight into games development to the reader.
The game allows for two players to play at the same time with both having their own separate inputs for moving, jumping and shooting. It also allows a winner to be determined through either reducing one players health to zero, reaching a score of 50 from collecting coins or having a higher score than the opponent when the timer reaches zero. Although this type of game doesn't seem new or inventive, I still believe it is a fun game to play much like other battle style games that are out there in the vast industry of video games.
\newline
In terms of requirements stated in section 1.4 Requirements, the end product complies with all the initial requirements specified. The game hits all the check boxes I feel it needed for it to be a fun short 2D 2 player game, allowing a small rest from reality and generally just to have fun.

\section{Learning Outcomes}
Throughout the scope of the project from start to finish, I have gained a substantial amount of new knowledge in the field of games development. From initial research and design to learning all the capabilities that Unity had to offer as well as some other game engines like Unreal Engine 4. The skills obtained and experiences earned will hopefully help me in the future if I can get into the career of video games development. My research gave me the ability to explore the present state of the process to make a video game. I have now seen first hand the importance of evaluating the work and research required to complete a project of this scale.
\newline
The skills learned have been priceless throughout the completion of the project. Even from researching how to do certain things on unity led me to see that there are so many ways to do one thing differently as all the developers out there have shown there own way of doing things and even I ended up doing certain things with my own kind of simpler twist on them. This module has also thought me how important meetings are in order to ensure that the deadlines can be met in time.

\section{Final Thoughts}
As the end of my 4 years in the Software Development course of GMIT is edging closer, I can happily hand up this project with a smile on my face and a sense of satisfaction in completing my goals. Even though I am no artist, I am happy with the way the game turned out after drawing my own art in a sketch art style as its not supposed to look good. The project was challenging from start to finish but reaching the end goal was such a rewarding experience and definitely a good way to get a feel of how the games industry works.

\section{A Word From The Developer}
 \textit{"I began studying programming 6 years ago in GTI for a games development course and i remember just getting a game to work without actually writing a line of code and thinking it was amazing. Fast forward to now where I was able to get a full game with code working all on my own, its still hard to believe. There has been a lot of struggles and late nights leading up to now but now that I'm nearing the end of the road I can safely say I have no regrets. This project could not have been done without the never ending help from my supervisors Dr. John Healy and Kevin O'Brien, they have my thanks. To whoever ends up playing this game, i hope it gives you even a little bit of fun, as the aim of this game from the start was to give the player just a bit of fun!"}