\chapter{System Evaluation}
After completing the development of my game, I had to look at evaluating its overall performance. The aim was to evaluate the game in the following areas:
\begin{itemize}
\item Robustness
\item Testing
\item Limitations
\item Results vs Objectives
\end{itemize}

\section{Robustness}
To measure the robustness of the game, I had decided to focus on this part of evaluation during the design and development of the project. I looked at the usability of the game itself in terms of the players control like jumping, moving and shooting, the UI elements appearing and disappearing when they should and in addition I gave friends a final build version of the game to test out.

\section{Testing}
Through using testing methods of white box testing and black box testing, I found that the project had reached a level design and functioning I had hoped for in the beginning when I set out to make this game. For white box testing, I tested the game myself in order to make sure everything was working the way that it was supposed to and that there were no major errors coming up on the console when running the game. For black box testing, I gave several different versions of builds to my friends to see if there where any bugs or problems playing the games. This allowed me to find any problems within the game that I may not have ran into when I was play testing the game myself.

\section{Limitations}
After the final build, which I sent to my friends to test out, it was discovered that there was an issue where if a player won the game by bringing the other players health down to zero and then went back to the main menu and started another game, the bullets would just go straight through the player and not damage them. After several hours of trying to fix the problem, I found no success. I came to the conclusion that it was not working because when the players health reached zero, it would stay at zero even though the hearts would show that the player had full health.

\section{Results V Objectives}
In the beginning, I had set out a number of objectives. In this section I will expand on these objectives. The project was made with the following objectives in mind:

\bigskip

\textbf {Make a Simple, yet fun to play game:} I feel that I did produce a fun simple game to play. After receiving feedback from the people I got to test the game they felt that it was a nice fun easy game to play around with. Using Unity made everything relatively easy as most things I had struggled with had tutorials on the unity website to help me along the way and it allowed me to provide a fun game.
\newline

\textbf {Dive into deeper learning into using game engines:} For the research part of the project I learned a lot about each different game engine and found that they are all great in their own way and I also now know which game engines to use in the future whether I will make a 2d game or a 3d game and which engine would produce the best results for my tastes.
\newline

\textbf {Complete the project using an efficient and effective approach:} As I had never done a project at this scale, I wanted to make sure I had all my ideas for the game finalized before I began working on the project. With being able to meet with my supervisor on a weekly basis or being able to contact him through email if for whatever reason I could not make the meeting was great in order to get feedback on my idea's and progress in the project.
\newline

\section{Overall Evaluation}
Overall, the game works as mostly intended and functions as a small fun game to play with a friend and it met my requirements that I set out in section 1.1 project objectives. Based on the tests I carried out by giving different build versions to friends, I was able to find bugs that I had not seen and fix them throughout development. Although I could have added improvements to the game like more levels or more characters, I was overall happy with the progress that I had made by the end. 

